Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-06-14 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Results of Grabich referenced

Current hurricane exposure assignments are often nonspecific and may lead to missclassification of exposure at the county-level [@Grabich2016]. Such missclassification can have important public health and economic implications.

@@

In comparison to the storm track, the areas of extreme rain and extreme wind can vary. For example, storms undergoing an extratropical transition can bring heavy rains to the left of the storm's center track, while extreme winds are more common to the right of the track [@Halverson2015].

>>>>

Current hurricane exposure assignments are often nonspecific and may lead to missclassification of exposure at the county-level [@Grabich2016]. Researchers have found heterogeneity in exposure assignments of counties in assessing multiple classification methods, both within and accross storms (i.e., storm dependent) [@Grabich2016]. Such missclassification can have important public health and economic implications.

@@

In comparison to the storm track, the areas of extreme rain and extreme wind can vary. For example, storms undergoing an extratropical transition can bring heavy rains to the left of the storm's center track, while extreme winds are more common to the right of the track [@Halverson2015, @Grabich2016].
